Title

### 2023-06-23 main.tex
Same as last commit with changes

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
{\color{red} Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation.}
\cpnote{no entiendo esta frase} 
\tbnote{Si, no está bien escrita. Cambiar por:}
{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
has to be constructed with only one parametrized rotation,
so it has to satisfy the conditions of theorem \ref{theorem2}.
}
Therefore, this implies that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

>>>>

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
has to be constructed with only one parametrized rotation,
so it has to satisfy the conditions of theorem \ref{theorem2}.
}
\cpnote{Sigue estando redundante. Dices que cuales se pueden implentar con 1pr circuit y que 
enticones tiene que ser construidas con un 1pr. Quizá integra las dos frases o has algo}
Therefore, this implies that the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.
